Adapting the Chumbley Score to Bullet Striations

### 2018-04-25 presentation/presentation.Rmd
pres thats it stop

Let $n_s$ and $n_d$ be the number of same shift and different shift windows $N = n_{s} + n_{d}$

The mann whitney U statistic is given by $U =\sum^{ns}{i=1}R{s}\left( i\right)$

>>>>

Let $n_s$ and $n_d$ be the number of same shift and different shift windows $$N = n_{s} + n_{d}$$

Additionally, let $R_s(i)$ and $R_d(j)$ be the ranks associated with the combined vector of correlations for the same-shift and different-shift correlations, for i = 1,2,...,$n_s$ and j = 1,2,...,$n_d$. Then the Mann–Whitney U-statistic is given by

The mann whitney U statistic is given by $$U =\sum^{n_s}_{i=1}R_{s}\left( i\right)$$
